---
title: "Moron colours"
author: "Ryan Morin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Existing palettes

Use the function `list_moron_pal` to get the names of all available palettes. Depending on how many are available, you can show the only (or your desired) palette size.

```{r,warning=F}
library(moroncolours)

list_moron_pal()

show_moron_pal("ledzep")

show_moron_pal("ledzep",6)

show_moron_pal("ledzep",9)

show_moron_pal("SgtPepper",9)

show_moron_pal("SgtPepper",12)

#palette inspired by a nice H&E image
show_moron_pal("HandE",12)

```


## Inspirations for palettes

Each palette is named after the image that inspired it. Below you will see some example images that were used to inspire the existing palettes.  

```{r}
library(imager)
im <- load.image(system.file('extdata/ledzep.jpg',package='moroncolours'))
plot(im, axes=FALSE)
```

## Making your own palettes

You can use the bundled inspirations or point the image_to_palette function to any image file to create new palettes on the fly. The example below uses two bundled images to create new palettes inspired by Aladdin and Frozen.

```{r}
#create a palette from the colours common in the Aladdin film
al_file = system.file('extdata/aladdin.jpg',package='moroncolours')
al_pal_16 = image_to_palette(al_file,16)
# new palette is automatically shown along with the corresponding hex codes
fr_file = system.file('extdata/frozen.jpg',package='moroncolours')
fr_pal_9 = image_to_palette(fr_file,9)

```

## Saving palettes permanently

Assuming we like these new palettes, then why not become a contributor to this package and add your new palette to it? This is a cinch to do. 

```{r,eval=F}
save_moron_pal(fr_pal_9,palette_name = "frozen",num_col = 9)
#this is not run in the vignette because it only works if run outside a markdown environment

```
